---
title: "Deliverable Part 1"
output: html_document
---


In my data set there is 26 variables and nearly 2 million obersvations. Some of the categorical variables that are going to be the most useful will be Crime.Code.Description, Crime.Code, and Area Name.


# SYNOPSIS

## In my Victim table, I have the variables;
-----------------------------------------
Report number, Age, Descent which describes what their ethnicity is, and sex


## In my CrimeDetails table I Have the Variables;
----------------------------------------------
Report_Number, Date_reported, 
Date_Occurred, Time_Occured, 
Area_Name, Crime_Code, 
Crime_Description, Premise_Code, 
Premise_Description which describe the premices where the crime took place, 
Weapon_Code, Weapon_Description, 
Status_Code, Status_Description which describes the status of the case, 
Crime_Code2-4 for if more than one crime was committed,
Address for where crime was committed, and Cross_Street for the cross street of the crime.

# Data Initialization

This is where I install the tidyverse and load in appropriate libraries for data wrangling

```{r}
#install.packages("tidyverse")
crime <- read.csv("~/CSCI385/PortfolioProject/crime-data-from-2010-to-present.csv", header=TRUE)
library("ggplot2")
library("tidyverse")
library("readr")
library("dplyr")
library("tidyr")
library("plyr")

## Clean up data, make victim, and crime tables, fix 0 or blanks with NA

Victim<-tibble(Report_Number = crime$DR.Number, Age = crime$Victim.Age, Descent = crime$Victim.Descent, Sex = crime$Victim.Sex)

CrimeDetails<-tibble(Report_Number = crime$DR.Number, Date_Reported = crime$Date.Reported, Date_Occurred = crime$Date.Occurred, Time_Occurred = crime$Time.Occurred, Area_Name = crime$Area.Name, Crime_Code = crime$Crime.Code, Crime_Description = crime$Crime.Code.Description, Premise_Code = crime$Premise.Code, Premise_Description = crime$Premise.Description, Weapon_Code = crime$Weapon.Used.Code, Weapon_Description = crime$Weapon.Description, Status_Code = crime$Status.Code, Status_Description = crime$Status.Description, Crime_Code2 = crime$Crime.Code.2, Crime_Code3 = crime$Crime.Code.3, Crime_Code4 = crime$Crime.Code.4, Address = crime$Address, Cross_Street = crime$Cross.Street)

Victim$Age[Victim$Age == "0"]<- NA
Victim$Sex[Victim$Sex == " "]<- NA
Victim$Descent[Victim$Descent == " "]<- NA
CrimeDetails$Weapon_Description[CrimeDetails$Weapon_Description == " "]<- NA
```
I tried to fix my dates so they's all be the same but I couldn't figure out how to get the function working
```{R}
#Fixing the date and times for my code

#CrimeDetails$Date_Reported<-as.POSIXlt(parse_datetime(as.character(CrimeDetails$Date_Reported), format = "%y-%m-%d"))
#typeof(CrimeDetails$Date_Reported)

#SELECT CAST(from_iso8601_timestamp(CrimeDetails$Date_Occured) as date())
#CrimeDetails$Date_Occurred<-as.POSIXlt(parse_datetime(as.character(CrimeDetails$Date_Occured) , format = "%y-%m-%d"))

#CrimeDetails$Time_Occurred<-as.POSIXlt(parse_datetime(CrimeDetails$Time_Occurred,format = "%H:%M %p"))
```
##The 3 most common crimes and areas were 
```{r}
mostCommon<-names(sort(summary(as.factor(CrimeDetails$Crime_Description)), decreasing=T)[1:3])
mostCommon

mostCommonArea<-names(sort(summary(as.factor(CrimeDetails$Area_Name)), decreasing=T)[1:3])
mostCommonArea
```
##Manipulating data

In this section I use the count function to get the total numbers of Stolen Vehicles, Battery, and burglary from vehicle. After that I created a function called getTheCountOf which takes 2 variables, crimeName and areaName and returns the number of reported incidents of crime in that area. After that I put them in a dataframe and gather them so I could properly graph them.

```{r}
countOfStolenVehicle<-count(CrimeDetails$Crime_Description[CrimeDetails$Crime_Description == "VEHICLE - STOLEN"])
countOfBattery<-count(CrimeDetails$Crime_Description[CrimeDetails$Crime_Description == "BATTERY - SIMPLE ASSAULT"])
countOfBurglary<-count(CrimeDetails$Crime_Description[CrimeDetails$Crime_Description == "BURGLARY FROM VEHICLE"])

getTheCount<-function(crimeName,areaName){
  CrimeCount<-count(CrimeDetails$Crime_Description[CrimeDetails$Crime_Description == crimeName & CrimeDetails$Area_Name == areaName])
  return(CrimeCount)
}

#Here is where i get the counts for the 3 top crimes on 77th Street
SeventhVehicle<-getTheCount("VEHICLE - STOLEN","77th Street")
SeventhBattery<-getTheCount("BATTERY - SIMPLE ASSAULT", "77th Street")
SeventhBurglary<-getTheCount("BURGLARY FROM VEHICLE","77th Street")

#Here is where I get the count of the top 3 crimes in the Southwest
SouthwestVehicle<-getTheCount("VEHICLE - STOLEN","Southwest")
SouthwestBattery<-getTheCount("BATTERY - SIMPLE ASSAULT","Southwest")
SouthwestBurglary<-getTheCount("BURGLARY FROM VEHICLE","Southwest") 

#Here is where I get the count of the top 3 crimes in N Hollywood
NHollywoodVehicle<-getTheCount("VEHICLE - STOLEN","N Hollywood")
NHollywoodBattery<-getTheCount("BATTERY - SIMPLE ASSAULT", "N Hollywood")
NHollywoodBurglary<-getTheCount("BURGLARY FROM VEHICLE", "N Hollywood")

#Here is where I get the count of the top 3 crimes in Pacific
#PacificVehicle<-getTheCount("VEHICLE - STOLEN","Pacific")
#PacificBattery<-getTheCount("BATTERY - SIMPLE ASSAULT", "Pacific")
#PacificBurglary<-getTheCount("BURGLARY FROM VEHICLE","Pacific")

#Here is where I get the count of top 3 crimes in Southeast
#SoutheastVehicle<-getTheCount("VEHICLE - STOLEN","Southeast")
#SoutheastBattery<-getTheCount("BATTERY - SIMPLE ASSAULT","Southeast")
#SoutheastBurglary<-getTheCount("BURGLARY FROM VEHICLE","Southeast")

Battery<-c(SeventhBattery$freq,SouthwestBattery$freq,NHollywoodBattery$freq)
Burglary<-c(SeventhBurglary$freq,SouthwestBurglary$freq,NHollywoodBurglary$freq)
VehicleTheft<-c(SeventhVehicle$freq,SouthwestVehicle$freq,NHollywoodVehicle$freq)


topCrimesAndAreas<-tibble(Area = mostCommonArea, CrimeType = mostCommon,Battery = Battery, Burglary = Burglary, VehicleTheft = VehicleTheft)

topCrimesAndAreas<-gather(topCrimesAndAreas, "CrimeType", "Count", 3:5)
```

#Visualizing some of my data

Here I use the data I tidied up and graphed the 3 top crimes in the 3 cities with the most reported Crime.

```{R}
#Plotting number of crimes vs Area
ggplot(topCrimesAndAreas, aes(fill = Area,x = CrimeType, y =Count)) + geom_bar(position = "dodge",stat = "identity")+geom_text(aes(label=Count), position=position_dodge(width=1.0), vjust=-.5)

```

Here you can see that 77th Street  led the charts in Battery and Vehicle theft. That was the most active area of reported crimes in my dataset.


