---
title: "Deliverable Part 1"
output: html_document
---
My second source is a website of crime statistics that compares LA crimes to the California and National averages.It has 9 different variables for types of crimes and each crime has 4 sections to put the number to scale.

#SYNOPSIS

##In my LA_crime table I will use the variables
-----------------------------------------------
Crime_type, Reported which is number of crimes reported, LA_Annual which is the annual amount of crime per 100k people

##In my Comparison table I will use the variables
-------------------------------------------------
Crime_type, CA_Annual which is the annual average per 100k people, and National_Annual which is the Annual average per 100k people.

#Data Initialization

Here is where I load in my libraries and data, I'm using a website so I have to web scrape the data.

```{r}
install.packages("tidyverse")
library("ggplot2")
library("tidyverse")
library("readr")
library("dplyr")
library("tidyr")
library("rvest")
library("caret")
library("caret")

#This is where I pull my first deliverable as my source
purl("Part1.Rmd", output = "part1.r")
source("part1.r")


my_url<-"https://www.areavibes.com/los+angeles-ca/crime/"
crime_html<-read_html(my_url)
#Statistics<- crime_html %>% html_nodes("tr:not(.header) > td:nth-child(1)") %>% html_text

Crime_type<- crime_html %>% 
            html_nodes("table.is-city tr:not(.header):not(.summary) > td:nth-child(1)") %>% 
  html_text()

Reported<- crime_html %>% 
            html_nodes("table.is-city tr:not(.header):not(.summary) > td:nth-child(2)") %>% 
  html_text()
Reported<-as.numeric(gsub(",","",Reported,fixed=TRUE))

LA_Annual<-crime_html %>% 
            html_nodes("table.is-city tr:not(.header):not(.summary) > td:nth-child(4)") %>% 
  html_text()
LA_Annual<-as.numeric(gsub(",","",LA_Annual,fixed=TRUE))

CA_Annual<-crime_html %>% 
            html_nodes("table.is-city tr:not(.header):not(.summary) > td:nth-child(5)") %>% 
  html_text()
CA_Annual<-as.numeric(gsub(",","",CA_Annual,fixed=TRUE))

National_Annual<- crime_html %>% 
            html_nodes("table.is-city tr:not(.header):not(.summary) > td:nth-child(6)") %>% 
  html_text()
National_Annual<-as.numeric(gsub(",","",National_Annual,fixed=TRUE))


LA_Crime<-tibble(Crime_type = Crime_type, Reported = Reported)

Comparison<-tibble(Crime_type = Crime_type, LA_Annual = LA_Annual, CA_Annual = CA_Annual, National_Annual = National_Annual)

Comparison<-gather(Comparison, "Locale", "Count",2:4)

ggplot(data = LA_Crime, aes(x = Crime_type, y = Reported)) + geom_bar(colour = "blue", stat = "identity",fill = "steelblue")+geom_text(aes(label=Reported), position=position_dodge(width=0.9), vjust=-0.25)

```
This Graph can easily show us the stats for reported crimes in 1 year in LA.


##In this next chunk of code I will compare LA's annual crime (per 100k citizens) to the rest of California, and the rest of America.
```{r}
ggplot(data = Comparison, aes(fill = Locale, x = Crime_type, y = Count)) + geom_bar(position = "dodge",stat = "identity") + geom_text(aes(label=Count), position=position_dodge(width=1.0), vjust=.1)

```
